Bricking up backdoors in Intrusion Detection Systems

### 2019-09-17 paper/paper.tex
Final changes to paper

\begin{abstract}
Interest in poisoning attacks and backdoors recently resurfaced for \gls{dl} applications. Several successful defense mechanisms have been recently proposed for \glspl{cnn}, for example in the context of autonomous driving. We show that visualization approaches can aid in identifying a backdoor independent of the used classifier. Surprisingly, we find that common defense mechanisms fail utterly to remove backdoors in \gls{dl} for \glspl{ids}. Finally, we conceive pruning-based approaches to remove backdoors for \glspl{dt} and \glspl{rf} and demonstrate their effectiveness for two different %several
network security datasets.
\end{abstract}

@@

There have been several works with the aim of increasing robustness of decision trees against attacks. \cite{biggio_bagging_2011} proposes a defense mechanism against poisoning that uses bagging to try to minimize the influence of a backdoor that is introduced in the training dataset. The method is applicable to \glspl{dt}. However, this approach cannot protect if a trained model is obtained from another (untrusted) party in which the other party might potentially have introduced a backdoor, which is the use case considered in this work. \cite{chen_robust_2019} develops a method to train \glspl{dt} with a tunable parameter that trades off accuracy against robustness against evasion attacks. \cite{russu_secure_2016} makes SVMs robust against evasion attacks and outlines a possibility to also apply it to \glspl{dt} and \glspl{rf}.
%\todo{Max: Unnecessary or should be moved to Related Work?}

>>>>

\begin{abstract}
Interest in poisoning attacks and backdoors recently resurfaced for \gls{dl} applications. Several successful defense mechanisms have been recently proposed for \glspl{cnn}, for example in the context of autonomous driving. We show that visualization approaches can aid in identifying a backdoor independent of the used classifier. Surprisingly, we find that common defense mechanisms fail utterly to remove backdoors in \gls{dl} for \glspl{ids}. Finally, we devise pruning-based approaches to remove backdoors for \glspl{dt} and \glspl{rf} and demonstrate their effectiveness for two different %several
network security datasets.
\end{abstract}

@@

%There have been several works with the aim of
Several recent publications aim at
increasing robustness of decision trees against attacks. \cite{biggio_bagging_2011} proposes a defense mechanism against poisoning that uses bagging to try to minimize the influence of a backdoor that is introduced in the training dataset. The method is applicable to \glspl{dt}. However, this approach cannot protect if a trained model is obtained from another (untrusted) party in which the other party might potentially have introduced a backdoor, which is the use case considered in this work. \cite{chen_robust_2019} develops a method to train \glspl{dt} with a tunable parameter that trades off accuracy against robustness against evasion attacks. \cite{russu_secure_2016} makes SVMs robust against evasion attacks and outlines a possibility to also apply it to \glspl{dt} and \glspl{rf}.
%\todo{Max: Unnecessary or should be moved to Related Work?}
